gavin_thesis_R

### 2024-06-25 _tex/index.tex
Built site for gh-pages

@@

@@

The raw DICOM files acquired from the scanning procedure were converted
to NIfTI (Neuroimaging Informatics Technology Initiative) format using
Chris Rorden's \texttt{dcmniix} tool. SWI magnitude data files were then
used to create subject-specific brain masks that would not erode the SSS
during QSM processing, an issue faced by our group in the past (X. Li et
al. 2016). A step-by-step summary of the pipeline used is shown in
Figure~\ref{fig-sample}.

@@

@@

@@

@@

>>>>

\textsubscript{Source:
\href{https://WeberLab.github.io/Chisep_CSVO2_Manuscript/index.qmd.html}{Article
Notebook}}

\textsubscript{Source:
\href{https://WeberLab.github.io/Chisep_CSVO2_Manuscript/index.qmd.html}{Article
Notebook}}

\textsubscript{Source:
\href{https://WeberLab.github.io/Chisep_CSVO2_Manuscript/index.qmd.html}{Article
Notebook}}

@@

\textsubscript{Source:
\href{https://WeberLab.github.io/Chisep_CSVO2_Manuscript/index.qmd.html}{Article
Notebook}}

@@

The raw DICOM files acquired from the scanning procedure were converted
to NIfTI (Neuroimaging Informatics Technology Initiative) format using
Chris Rorden's \texttt{dcmniix} tool. SWI magnitude data files were then
used to create subject-specific brain masks that would not erode the SSS
during QSM processing, an issue faced by our group in the past (X. Li et
al. 2016). A step-by-step summary of the pipeline used is shown in
Figure~\ref{fig-graph}.

@@

\textsubscript{Source:
\href{https://WeberLab.github.io/Chisep_CSVO2_Manuscript/notebooks/Figures-preview.html\#cell-fig-graph}{Python
Figures}}

@@

\textsubscript{Source:
\href{https://WeberLab.github.io/Chisep_CSVO2_Manuscript/notebooks/Figures-preview.html\#cell-fig-sample}{Python
Figures}}

@@

\textsubscript{Source:
\href{https://WeberLab.github.io/Chisep_CSVO2_Manuscript/notebooks/gavin_thesis_markdown-preview.html\#cell-fig-methodplot}{gavin\_thesis\_R}}

@@

\textsubscript{Source:
\href{https://WeberLab.github.io/Chisep_CSVO2_Manuscript/notebooks/gavin_thesis_markdown-preview.html\#cell-fig-regionplot}{gavin\_thesis\_R}}

### 2024-06-25 notebooks/gavin_thesis_markdown.qmd
Built site for gh-pages

Load main dataframe (change directory as needed)
*note: columns titled with with "Gavin_x_x" contain QSM data
```{r}
newdata <- read.csv("newdata.csv")
```

@@

Wilcox test for p-values and 95% CI - table 3.2
```{r}
#SSS Chi
wilcox.test(newdata$Gavin_SSS_Chi, newdata$Chisep_SSS_Chi,
            paired = TRUE, conf.int = TRUE)

#SSS SvO2
wilcox.test(newdata$Gavin_SSSVein_CSvO2, newdata$Chisep_SSSVein_CSvO2,
            paired = TRUE, conf.int = TRUE)

#CCV Chi
wilcox.test(newdata$Gavin_IntVein_Chi, newdata$Chisep_IntVein_Chi, paired = TRUE,
            conf.int = TRUE)

#CCV SvO2
wilcox.test(newdata$Gavin_IntVein_CSvO2, newdata$Chisep_IntVein_CSvO2,
            paired = TRUE, conf.int = TRUE)
```

@@

Figure 3.1
*note: "****" in panels were added outside of R
```{r}
#| echo = FALSE
m1 <- ggwithinstats(
  data = comp_CCV_chi,
  x = Method,
  y = Chi,
  results.subtitle = FALSE,
  title = "(A)",
  subtitle = "Central Cerebral Veins",
  type = "nonparametric",
  centrality.plotting = FALSE,
  point.path.args = list(linewidth = 0.25, linetype = "solid")
)

m2 <- ggwithinstats( 
  data = comp_SSS_chi,
  x = Method,
  y = Measured.Susceptibility, 
  ylab = "Chi",
  results.subtitle = FALSE,
  title = "",
  subtitle = "Superior Sagittal Sinus",
  type = "nonparametric", 
  centrality.plotting = FALSE,
  point.path.args = list(linewidth = 0.25, linetype = "solid")
)

m3 <- ggwithinstats(
  data = comp_CCV_SvO2,
  x = Method,
  y = Oxygen.Saturation,
  ylab = "SvO2",
  results.subtitle = FALSE,
  title = "(B)",
  subtitle = "Central Cerebral Veins",
  type = "nonparametric",
  centrality.plotting = FALSE,
  point.path.args = list(linewidth = 0.25, linetype = "solid")
)

m4 <- ggwithinstats(
  data = comp_SSS_SvO2,
  x = Method,
  y = Oxygen.Saturation,
  pairwise.display = "all",
  ylab = "SvO2",
  results.subtitle = FALSE,
  title = "",
  subtitle = "Superior Sagittal Sinus",
  type = "nonparametric",
  centrality.plotting = FALSE,
  point.path.args = list(linewidth = 0.25, linetype = "solid")
)

combine_plots(
  plotlist = list(m1, m2, m3, m4),
  plotgrid.args = list(nrow = 2)
)
```

Figure 3.2
*note: "****" in panels (a) and (b) were added outside of R
```{r}
#| echo = FALSE
p1 <- ggwithinstats(
  data = comp_legit_starfsl,
  x = Vein,
  y = Chi,
  pairwise.display = "all",
  results.subtitle = FALSE,
  xlab = "Region",
  ylab = "Chi",
  title = "(A)",
  type = "nonparametric",
  centrality.plotting = FALSE,
  point.path.args = list(linewidth = 0.25, linetype = "solid"),
  point.args = list(color = "#D95F02") 
)

p2 <- ggwithinstats(
  data = comp_SSS_IntVein_CSvO2,
  x = Vein,
  y = CSvO2,
  pairwise.display = "all",
  results.subtitle = FALSE,
  xlab = "Region",
  ylab = "SvO2",
  title = "(B)",
  type = "nonparametric",
  centrality.plotting = FALSE,
  point.path.args = list(linewidth = 0.25, linetype = "solid"),
  point.args = list(color = "#D95F02")
)

p3 <- ggwithinstats(                     #boxplot of chi comparison between regions
  data = comp_chisep_chi,
  x = Vein,
  y = Chi, 
  pairwise.display = "all",
  results.subtitle = FALSE,
  xlab = "Region",
  ylab = "Chi",
  title = "(C)",
  subtitle = "                                                n.s.",
  type = "nonparametric", 
  centrality.plotting = FALSE,
  point.path.args = list(linewidth = 0.25, linetype = "solid"),
  point.args = list(color = "#1B9E77")
)

p4 <- ggwithinstats(                    #boxplot of svo2 comparison between regions
  data = comp_chisep_CSvO2,
  x = Vein,
  y = CSvO2, 
  pairwise.display = "all",
  results.subtitle = FALSE,
  xlab = "Region",
  ylab = "SvO2",
  title = "(D)",
  subtitle = "                                                n.s.",
  type = "nonparametric",
  centrality.plotting = FALSE,
  point.path.args = list(linewidth = 0.25, linetype = "solid"),
  point.args = list(color = "#1B9E77")
)

combine_plots(
  plotlist = list(p1, p2, p3, p4),
  plotgrid.args = list(nrow = 2)
)
```

@@

```{r}
 p1 <- ggwithinstats(
  data = comp_legit_starfsl,
  x = Vein,
  y = Chi,
  results.subtitle = FALSE,
  type = "p",
  pairwise.display = "all",
  bf.message = FALSE,
  xlab = "Region",
  ylab = "Chi",
  centrality.plotting = FALSE,
  point.path.args = list(linewidth = 0.25, linetype = "solid"),
  point.args = list(color = "#D95F02")) + 
  ggplot2::annotate("text", x=1.5, y=(max(comp_legit_starfsl$Chi)*1.05), size=4, label = "***")

p2 <- ggwithinstats(
  data = comp_SSS_IntVein_CSvO2,
  x = Vein,
  y = CSvO2,
  results.subtitle = FALSE,
  type = "p",
  pairwise.display = "all",
  bf.message = FALSE,
  xlab = "Region",
  ylab = "SvO2",
  centrality.plotting = FALSE,
  point.path.args = list(linewidth = 0.25, linetype = "solid"),
  point.args = list(color = "#D95F02")
) + 
  ggplot2::annotate("text", x=1.5, y=(max(comp_SSS_IntVein_CSvO2$CSvO2)*1.05), size=4, label = "***")

p3 <- ggwithinstats(                     #boxplot of chi comparison between regions
  data = comp_chisep_chi,
  x = Vein,
  y = Chi, 
  results.subtitle = FALSE,
  pairwise.display = "all",
  bf.message = FALSE,
  xlab = "Region",
  ylab = "Chi",
  centrality.plotting = FALSE,
  point.path.args = list(linewidth = 0.25, linetype = "solid"),
  point.args = list(color = "#1B9E77")
) +
  ggplot2::annotate("text", x=1.5, y=(max(comp_chisep_chi$Chi))*1.05, size=4, label = "n.s.")

p4 <- ggwithinstats(                    #boxplot of svo2 comparison between regions
  data = comp_chisep_CSvO2,
  x = Vein,
  y = CSvO2, 
  results.subtitle = FALSE,
  pairwise.display = "all",
  bf.message = FALSE,
  xlab = "Region",
  ylab = "SvO2",
  type = "nonparametric",
  centrality.plotting = FALSE,
  point.path.args = list(linewidth = 0.25, linetype = "solid"),
  point.args = list(color = "#1B9E77")
) +
  ggplot2::annotate("text", x=1.5, y=(max(comp_chisep_CSvO2$CSvO2)*1.05), size=4, label = "n.s.")

(patch1 <- (p1 + p2)/(p3 + p4))
# patch1
# ggsave('figure.png', patch1)
```

```{r}
#| label: fig-regionplot
#| fig-width: 8
#| fig-height: 5
#| fig-cap: "rmarkdown test figure"
patch1
```

>>>>

Load main dataframe (change directory as needed)
*note: columns titled with with "Gavin_x_x" contain QSM data
```{r}
newdata <- read.csv("newdata.csv")

signif="***"
notsig="n.s."

sigfunc <- function(pval) {
if (pval < 0.05){
  label = signif
} else {
    label = notsig
}
  return (label)
}
```

@@

@@

Figure 3.1
```{r}
#| echo = FALSE
label = sigfunc(SSSChi.t$p.value)
m1 <- ggwithinstats(
  data = comp_CCV_chi,
  x = Method,
  y = Chi,
  ylab = "Chi (ppm)",
  results.subtitle = FALSE,
  type = "p",
  pairwise.display = "all",
  bf.message = FALSE,
  centrality.plotting = FALSE,
  point.path.args = list(linewidth = 0.25, linetype = "solid")) +
  ggplot2::annotate("text", x=1.5, y=(max(comp_CCV_chi$Chi)*1.05), size=4, label = label)

label = sigfunc(SSSSvO2.t$p.value)
m2 <- ggwithinstats( 
  data = comp_SSS_chi,
  x = Method,
  y = Measured.Susceptibility, 
  ylab = "Chi (ppm)",
  results.subtitle = FALSE,
  type = "p",
  pairwise.display = "all",
  bf.message = FALSE,
  centrality.plotting = FALSE,
  point.path.args = list(linewidth = 0.25, linetype = "solid")) +
  ggplot2::annotate("text", x=1.5, y=(max(comp_SSS_chi$Measured.Susceptibility)*1.05), size=4, label = label )

label = sigfunc(CCVChi.t$p.value)
m3 <- ggwithinstats(
  data = comp_CCV_SvO2,
  x = Method,
  y = Oxygen.Saturation,
  ylab = "SvO2 (%)",
  results.subtitle = FALSE,
  type = "p",
  pairwise.display = "all",
  bf.message = FALSE,
  centrality.plotting = FALSE,
  point.path.args = list(linewidth = 0.25, linetype = "solid") ) +
  ggplot2::annotate("text", x=1.5, y=(max(comp_CCV_SvO2$Oxygen.Saturation)*1.05), size=4, label = label )

label = sigfunc(CCVSvO2.t$p.value)
m4 <- ggwithinstats(
  data = comp_SSS_SvO2,
  x = Method,
  y = Oxygen.Saturation,
  ylab = "SvO2 (%)",
  results.subtitle = FALSE,
  type = "p",
  pairwise.display = "all",
  bf.message = FALSE,
  centrality.plotting = FALSE,
  point.path.args = list(linewidth = 0.25, linetype = "solid") ) +
  ggplot2::annotate("text", x=1.5, y=(max(comp_SSS_SvO2$Oxygen.Saturation)*1.05), size=4, label = label )
(patch1 <- (m1 + m2)/(m3 + m4) + 
  plot_annotation(tag_levels = 'A') & 
  theme(plot.tag = element_text(size = 10)))
```

```{r}
#| label: fig-methodplot
#| fig-width: 8
#| fig-height: 5
#| fig-cap: "Vein-specific susceptibility and oxygen saturation values by method. (A, B) contains violin plots comparing subject χ (ppm) acquired from QSM (A) and its paramagnetic component (B); (C, D) contains violin plots comparing subject SvO2 (%) acquired from QSM (C) and its paramagnetic component (D). Raw data points from paramagnetic maps are shown as filled green circles and raw data points from QSM are shown as filled orange circles. Each line connects the raw data points of a single subject. (***) indicates P<0.05."
patch1
```

# Region analysis: Chi and CSvO2

```{r}
#SSS Chi
RegionQSMChi.t <- tidy(t.test(newdata$Gavin_IntVein_Chi, newdata$Gavin_SSS_Chi, 
            paired = TRUE, conf.int = TRUE))

#SSS SvO2
RegionQSMSvO2.t <- tidy(t.test(newdata$Gavin_IntVein_CSvO2, newdata$Gavin_SSSVein_CSvO2,
            paired = TRUE, conf.int = TRUE))

#CCV Chi
RegionChisepChi.t <- tidy(t.test(newdata$Chisep_IntVein_Chi, newdata$Chisep_SSS_Chi, paired = TRUE,
            conf.int = TRUE))

#CCV SvO2
RegionChisepSvO2.t <- tidy(t.test(newdata$Chisep_IntVein_CSvO2, newdata$Chisep_SSSVein_CSvO2,
            paired = TRUE, conf.int = TRUE))
```

```{r}

label = sigfunc(RegionQSMChi.t$p.value)
 p1 <- ggwithinstats(
  data = comp_legit_starfsl,
  x = Vein,
  y = Chi,
  results.subtitle = FALSE,
  type = "p",
  pairwise.display = "all",
  bf.message = FALSE,
  xlab = "Region",
  ylab = "Chi (ppm)",
  centrality.plotting = FALSE,
  point.path.args = list(linewidth = 0.25, linetype = "solid"),
  point.args = list(color = "#D95F02")) + 
  ggplot2::annotate("text", x=1.5, y=(max(comp_legit_starfsl$Chi)*1.05), size=4, label = label)

label = sigfunc(RegionQSMSvO2.t$p.value)
p2 <- ggwithinstats(
  data = comp_SSS_IntVein_CSvO2,
  x = Vein,
  y = CSvO2,
  results.subtitle = FALSE,
  type = "p",
  pairwise.display = "all",
  bf.message = FALSE,
  xlab = "Region",
  ylab = "SvO2 (%)",
  centrality.plotting = FALSE,
  point.path.args = list(linewidth = 0.25, linetype = "solid"),
  point.args = list(color = "#D95F02")
) + 
  ggplot2::annotate("text", x=1.5, y=(max(comp_SSS_IntVein_CSvO2$CSvO2)*1.05), size=4, label = label)

label = sigfunc(RegionChisepChi.t$p.value)
p3 <- ggwithinstats(                     #boxplot of chi comparison between regions
  data = comp_chisep_chi,
  x = Vein,
  y = Chi, 
  results.subtitle = FALSE,
  pairwise.display = "all",
  bf.message = FALSE,
  xlab = "Region",
  ylab = "Chi (ppm)",
  centrality.plotting = FALSE,
  point.path.args = list(linewidth = 0.25, linetype = "solid"),
  point.args = list(color = "#1B9E77")
) +
  ggplot2::annotate("text", x=1.5, y=(max(comp_chisep_chi$Chi))*1.05, size=4, label = label)

label = sigfunc(RegionChisepSvO2.t$p.value)
p4 <- ggwithinstats(                    #boxplot of svo2 comparison between regions
  data = comp_chisep_CSvO2,
  x = Vein,
  y = CSvO2, 
  results.subtitle = FALSE,
  pairwise.display = "all",
  bf.message = FALSE,
  xlab = "Region",
  ylab = "SvO2 (%)",
  type = "nonparametric",
  centrality.plotting = FALSE,
  point.path.args = list(linewidth = 0.25, linetype = "solid"),
  point.args = list(color = "#1B9E77")
) +
  ggplot2::annotate("text", x=1.5, y=(max(comp_chisep_CSvO2$CSvO2)*1.05), size=4, label = label)

(patch2 <- (p1 + p2)/(p3 + p4) + 
  plot_annotation(tag_levels = 'A') & 
  theme(plot.tag = element_text(size = 10)))
```

```{r}
#| label: fig-regionplot
#| fig-width: 8
#| fig-height: 5
#| fig-cap: "Inter-venous comparisons of susceptibility and oxygen saturation. Violin plots comparing (A, C) χ (ppm) and (B, D) SvO2 (%) between the CCV and the SSS. Panels (A) and (B) used data acquired from QSM, and its raw data points are shown as filled orange circles. Panels (C) and (D) used data acquired from paramagnetic maps, and its raw data points are shown as filled green circles. Each line connects the raw data points of a single subject. (***) indicates p<0.05; (n.s.) indicates no significant difference."
patch2
```

@@
